\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-09-22 latex/whitepaper/article.tex
whitepaper draft

The Syscoin Foundation will allocate \$20M SYS into SYS Labs. At approx. \$27M USD peak valuation, SYS Labs will execute the master node yield strategy using the rewards (see Table 6). This will enable liquidity events which investors of SYS Labs can execute on through token warrants in exchange for equity. Masternode ROI will be used to deposit into DAOSYS which will be used to fund ecosystem initiatives as well as pay out token warrants to SYS Labs investors looking to exit. Analysis on Masternode ROI based on price modelling through to year 2028; see here. Analysis on DAOSYS ROI based on price modelling through to year 2025 (not including value created through lending to builders to build ecosystem objectives); see \cite{DAOSim22}.

>>>>

The Syscoin Foundation will allocate \$20M SYS into SYS Labs. At approx. \$27M USD peak valuation, SYS Labs will execute the master node yield strategy using its rewards. This will enable liquidity events which investors of SYS Labs can execute on through token warrants in exchange for equity. Masternode ROI will be used to deposit into DAOSYS which will be used to fund ecosystem initiatives as well as pay out token warrants to SYS Labs investors looking to exit. Analysis on Masternode ROI based on price modelling through to year 2028; see \cite{DAOSim22} for Jupyter notebook. Analysis on DAOSYS ROI based on price modelling through to year 2025 (not including value created through lending to builders to build ecosystem objectives); see \cite{DAOSim22}.
